Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-26 General WLD combinatorics.tex
finish propagator pov for Lem 3.7

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$. Write $(p, <_i)$ be the same propagator with a direction induced by the linear ordering $<_i$. Then \bas V_{in}(p, <_i) = \{a \in [n] | i+1 <_i a <_i j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_i) = \{a \in [n] | j+1 <_j a <_j i \} \;.\eas the region {\bf outside }$p$. 
\end{dfn}

Similarly, we may associate the ordering $<_j$ to $p$, in which case $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.

@@

Now suppose $q_{r} = (i_r, k_r) $ exists by the induction hypothesis, oriented $(q_r, <_{i_r})$ as above. Call the restriction to the propagators inside $q_r$ in this orientation (including itself) $W_r := W|_{\cP_{in} \cup q_r}$ does not contain any $p_i$ for $i\leq r$. By the original hypotheses on $W$ every vertex in $V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $V(q_r)$ because these vertices support $q_r$. By construction, the remaining vertices of $W|_{\cP_{in} \cup p}$, i.e. $V_{out}(q_r)$ are non-supporting.

@@

Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ such that $p_{r+1}\in \cP_{out}(q_r, <_{i_r})$ on the outside.

*******STOPPED HERE (OLD K BELOW)********

There are two cases to consider.
The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-2$.  Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.  The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.  Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.  Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $q_r$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
Therefore the first case cannot occur.

The second case is that either at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$, or both ends lie in $[i_r, i_r+3]$ or $[k_r-3, k_r]$; these situations all behave similarly.  Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ where either the edge $j_{r+1}+2$ is contained in $[i_r+3, k_r-3]$ or $j_{r+1}+2 = i_r+2$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$ in both situations), there is some propagator $t$ with one end in $[j_{r+1}+3, j_{r+1}+5]$ and length $\geq 4$.  By noncrossingness $t$ is contained in $q_{r}$.  $t$ does not contain $p_{r+1}$ by minimality and so we may set $q_{r+1} = t$ to continue the induction.

>>>>

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$. Write $(p, <_a)$ be the same propagator with a direction induced by the linear ordering $<_a$. Then \bas V_{in}(p, <_a) = \{b \in [n] | i+1 <_a b <_a j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_a) = \{b \in [n] | j+1 <_a b <_a i \} \;.\eas the region {\bf outside }$p$. 
\end{dfn}

Depending on the ordering associated to $p$, the vertices on the inside and outside chagne. In particular, for $p = (i,j)$, $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.

@@

Now suppose $q_{r} = (i_r, k_r) $ exists by the induction hypothesis, oriented $(q_r, <_{i_r})$ as above. For the rest of this proof, we assume this orientation as read, and drop the $<_{i_r}$ from the notation. Call the restriction to the propagators inside $q_r$ in this orientation (including itself) $W_r := W|_{\cP_{in} \cup q_r}$ does not contain any $p_i$ for $i\leq r$. By the original hypotheses on $W$ every vertex in $V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $V(q_r)$ because these vertices support $q_r$. By construction, the remaining vertices of $W|_{\cP_{in} \cup p}$, i.e. $V_{out}(q_r)$ are non-supporting.

@@

Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ such that $p_{r+1}\in \cP_{out}(q_r)$ is on the outside.

There are two cases to consider.
In the first case define $p_{r+1} = (j_{r+1}, j_{r+1}+2)$  with $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1} \leq k_{r}$.  Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.  Let $s$ be a propagators in $\cP_{in}(q_r)$ such that $p_{r+1}$ is not an interior propagator in the $<_{i_r}$ ordering: $p_{r+1} \not \in \cP_{in}(s, <{i_r})$. If it exists, $s = (i_s, j_s)$ must satisfy $i_r \leq i_s \leq j_s \leq i_r+2$ or $k_r-2 \leq i_s \leq j_s \leq k_r$ and hence be of length 2.  Therefore, if $\cP_{in}(q_r)$ contains a propagator $t$ of length $\leq 4$, $p_{r+1}$ must lie on its inside in the $<i_r$ ordering ( $p_{r+1} \in \cP_{in}(q_r, <_{i_r})$) which is impossible my minimality.  Therefore, if $\cP_{in}(q_r)$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
Therefore the first case cannot occur.

In the second case, write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$. Either at least $i_r+3 \leq j_{r+1} +2 \leq k_r-3$, or $i_r = j_{r+1}$ or $k_r-2 = j_{r+1}$; these situations all behave similarly.  By symmetry we consider only the first two cases. Not that since $j_{r+1}+4 \leq k_r-1$ in both cases, $j_{r+1}+4 \in V_{in}(q_r)$, and is thus supported. Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s}, there is some propagator $t \in \Prop(j_{r+1}+4)$ with \hlfix{length $\geq 4$.  By noncrossingness $t$ is inside $q_r$, $t \in \cP_{in}(q_r)$, and $p_{r+1}$ is outside $t$, $p_{r+1} \not \in \cP_{in}(t, <_{i,r})$ by minimality. So we may set $q_{r+1} = t$ to continue the induction.  }{Hope I haven't broken things, but I don't follow why $\ell(t)\geq 4$ or $p_{r+1} \not \in \cP_{in}(t, <_{i,r})$}
